---
title: "Field Baker's day at campus"
author: "Dottie/Jacky Maya"
date: "4/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TSP)
```

Young Field Baker is planning his trip to CSUB campus.  He must make 5 stops and one visit to a restroom.  He starts and ends the day at the bus stop on campus

The stops he must make and the North, East coordinates of each are givnen in the following table: (units are Cubits)

   Location     |  coordinates (N, W)
   -------------|--------------------
   Bus stop     |  25, 200
   Engineering Complex |  110, 160
   Dorthy Donahue Building  |  250, 200
   Student Union  |  250, 300
   Walter Stern Library  | 300, 250
   Administration Building | 260  , 50
   
   In addition he must one stop at a  restroom; the available restrooms are at locations (200,160), (340,110), and (280,290)
   
   Find the shortest route freshman Field can take on this visit.  Only 1 restroom stop
   
   
```{r}

```

   
   
   